---
title: "CCA2022"
author: "Lan Phan"
date: "5/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Packages**
```{r}
library(haven)
library(tidyverse)
library(dplyr)
dat <- read_sav("~/Desktop/Academics/PhD Research/CCA:CCO/CCA Instructor Survey/Survey 2 for R.sav")
```

**Data Transformation**
```{r}
dat <- select(dat, -starts_with("Old"), -starts_with("OLD"))
dim(dat)

#######################
#Create New Variables
#######################

###IVs
dat$PETotal <- ((dat$PEQ32 + dat$PEQ33 + dat$PEQ34 + dat$PEQ35 + dat$PEQ36 + dat$PEQ37 + dat$PEQ38 + dat$PEQ39)/8)

#IV1 is Agent Cultural Embeddedness
dat$IV1 <- ((dat$AgentQ67 + dat$AgentQ66 + dat$AgentQ68 + dat$AgentQ69 + dat$AgentQ70)/5)

#IV2 is basically PETotal/ Process

#IV3 = Stakeholder Western to Eastern Value
dat$IV3 <- ((dat$StakeQ53 + dat$StakeQ54 + dat$StakeQ57 + dat$StakeQ58 + dat$StakeQ60)/5)

#IV4 = Agent Western to Eastern Value
dat$IV4 <- ((dat$AgentQ79 + dat$AgentQ80)/2)

#IV5 = Contextual Challenges & Demands
dat$IV5 <- ((dat$ContextQ23+dat$ContextQ25+dat$StakeQ62)/3)

#IV6 = Cultural Constraints & Tightness
dat$IV6 <- ((dat$ContextQ26+dat$ContextQ27+dat$ContextQ28)/3)

#IV7= Agent Tolerance for Ambiguity
dat$IV7 <- ((dat$AgentQ73+dat$AgentQ76)/2)



###DVs

#DV1 = Self-Rated Effectiveness
dat$DV1 <- ((dat$OUTQ81_3 + dat$OUTQ81_4 + dat$OUTQ81_8 + dat$OUTQ81_9 + dat$OUTQ81_14)/5)

#DV2 = Self-Rated Cultural Appropriateness
dat$DV2 <- ((dat$OUTQ81_5 + dat$OUTQ81_7 + dat$OUTQ81_20 + dat$OUTQ81_21 + dat$OUTQ81_25 + dat$OUTQ81_27)/6)

#DV3 = Sustainability
dat$DV3 <- ((dat$OUTQ81_15 + dat$OUTQ81_16 + dat$OUTQ81_26 + dat$OUTQ81_34)/4)

#DV4 = Culture Sensitivity
dat$DV4 <- ((dat$OUTQ81_35 + dat$OUTQ81_36 + dat$OUTQ81_37 + dat$OUTQ81_38)/4)

#DV5= Cost-Effectiveness
dat$DV5 <- ((dat$OUTQ81_10 + dat$OUTQ81_11)/2)

#DV6 = Efficiency
dat$DV6 <- ((dat$OUTQ81_6 + dat$OUTQ81_12 + dat$OUTQ81_13)/3)

#Also 2 qualitative DVs DV8_QualiGenEff and DV9_QualiSustain
```

**What are the main factors that motivate agents to use a P vs. E Approach?**
```{r}
#Correlations
library(Hmisc)
datcorr <- select(dat, IV1, IV3, IV4, IV5, IV6, IV7, PETotal)

# Correlations with P values to see significance
correlations <- rcorr(as.matrix(select(datcorr, 1:6, 7)))

# Visualize the correlations; insignificant are left blank
library(corrplot)
corrplot(correlations$r, type = "upper", order = "hclust",
         p.mat = correlations$r, sig.level = 0.05, insig = "blank")
#seems like all has significant negative correlations

#Check for actual correlations
cor.test(dat$IV1, dat$PETotal) #p <.001; r = -.35
#The more embedded the instructor is, the more likely they will use an elicitive approach

cor.test(dat$IV3, dat$PETotal) # p<.01, r = -.28
#The more Western the stakeholder are perceived to be, the more likely they will use an elicitive approach

cor.test(dat$IV4, dat$PETotal) #n.s.

cor.test(dat$IV5, dat$PETotal) # p <.01, r = -.29
# The less challenging and demanding the context is (mono-cultural, have no functional systems, and local decision making are unjust)
# the more likely an elicitive approach will be used. 

cor.test(dat$IV6, dat$PETotal) # p<.001, r = -.40
#In looser culture with fewer constraints, instructors are more likely to use elicitive methods

cor.test(dat$IV7, dat$PETotal) # p<.001, r = .31
#The higher the agent tolerance for ambiguity, the more likely they will use an elicitive approach
```

**In general, are E approaches more effective, sustainable, and satisfying than P?**
```{r}
###################
### One-way ANOVA
####################
library(car)
library(emmeans) #for pairwise comparison later

#Create P-E Group Levels
summary(dat$PETotal) #use these numbers to divide into groups
dat$PEGroup <- cut(dat$PETotal,
                   breaks = c(-Inf, 3.25, 4.625, Inf),
                   levels = c(1,2,3),
                   labels = c("P", "H", "E"))

summary(dat$PEGroup) #P has 38; H has 51; E has 28
#Create weights for the groups due to uneven sizes
library(plyr)
dat$PEGroupWts <- revalue(dat$PEGroup, c("P"="1.34", "H"="1", "E"="1.82"))
dat$PEWts <- as.numeric(as.vector(dat$PEGroupWts)) #turn into numeric

#Change to effect coding instead of dummy coding
options()$contrasts
options(contrasts = c("contr.sum", "contr.poly"))

####### testing for the DVs against PE ###########

### DV1 ###
#full model
lmDV1F <- lm(DV1 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV1F)

Anova(lmDV1F, type = 3)
# The PE group does not have significant effect on DV1 


######DV2#######
lmDV2F <- lm(DV2 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV2F)
#n.s.

######DV3#######
lmDV3F <- lm(DV3 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV3F)
#n.s

######DV4#######
lmDV4F <- lm(DV4 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV4F)
#n.s.


####DV5#######
lmDV5F <- lm(DV5 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV5F)
#n.s.

######DV6#######
lmDV6F <- lm(DV6 ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV6F)
#F(2,111) = 4.69; p = .01
#significant
Anova(lmDV6F, type = 3)
#significant differences among PE groups

# Now follow up with pairwise comparisons.
emm6 <- emmeans(object = lmDV6F,
                specs = ~ PEGroup) #only need the full model here
#want groups to be broken up by P-E Approach

emm6 # individual means 

pairs(x = emm6, 
      adjust = "Bonferroni")  # Bonferroni-adjusted. Ok to interpret.
#Significant difference between P (M = 4.28) and E (mean = 3.48) (p <.01)
#n.s. for hybrid (m = 3.97)
#Elicitive methods are significantly less efficient than Prescriptive


####Coded Effectiveness#######
lmDV8F <- lm(DV8_QualiGenEff ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV8F)
#n.s.

######Coded Sustainability & Learning#####
lmDV9F <- lm(DV9_QualiSustain ~ PEGroup, data = dat, weights = PEWts) #using weighted analysis
summary(lmDV9F)
#n.s.


#Only DV6 (Efficiency) has significant differences among the 3 groups
#Interpretation: There is no universally effective/ sustainable methods
#without controlling for contextual factors 
```

**Controlling for contextual factors, are E approaches more effective, sustainable, and satisfying than P?**
```{r}
####################################
#Multiple Hierarchical Regression
####################################

#Check for correlations
cor.test(dat$PETotal, dat$DV1) #ns
cor.test(dat$PETotal, dat$DV2) #ns
cor.test(dat$PETotal, dat$DV3) #ns
cor.test(dat$PETotal, dat$DV4) #ns
cor.test(dat$PETotal, dat$DV5) #ns
cor.test(dat$PETotal, dat$DV6) #significant at p =.03, r = -.20

###DV1#######
AControl1 <- lm(DV1~ IV1+IV3+IV4+IV5+IV6+IV7, data = dat) #Control for context differences
summary(AControl1)

ModelPE1 <- lm(DV1~IV1+IV3+IV4+IV5+IV6+IV7 + PETotal, data = dat)
summary(ModelPE1) #PE Significant


anova(AControl1, ModelPE1) #Model 2 has significant differences
#When controlling for external factors, P-E Process significantly predict DV1


###DV2#######
AControl2 <- lm(DV2~ IV1+IV3+IV4+IV5+IV6, data = dat) #Control for context differences
summary(AControl2)

ModelPE2 <- lm(DV2~IV1+IV3+IV4+IV5+IV6 + PETotal, data = dat)
summary(ModelPE2) #PE Significant


anova(AControl2, ModelPE2) #Model 2 has significant differences
#When controlling for external factors, P-E Process significantly predict DV2

###DV3#######
AControl3 <- lm(DV3~ IV1+IV3+IV4+IV5+IV6+IV7, data = dat) #Control for context differences
summary(AControl3)

ModelPE3 <- lm(DV3~IV1+IV3+IV4+IV5+IV6+IV7 + PETotal, data = dat)
summary(ModelPE3) #PE Significant


anova(AControl3, ModelPE3) #Model 2 has significant differences
#When controlling for external factors, P-E Process significantly predict DV3

###DV4#######
AControl4 <- lm(DV4~ IV1+IV3+IV4+IV5+IV6+IV7, data = dat) #Control for context differences
summary(AControl4)

ModelPE4 <- lm(DV4~IV1+IV3+IV4+IV5+IV6+IV7 + PETotal, data = dat)
summary(ModelPE4) #PE Significant


anova(AControl4, ModelPE4) #Model 2 has significant differences
#When controlling for external factors, P-E Process significantly predict DV1


###DV5#######
AControl5 <- lm(DV5~ IV1+IV3+IV4+IV5+IV6+IV7, data = dat) #Control for context differences
summary(AControl5)

ModelPE5 <- lm(DV5~IV1+IV3+IV4+IV5+IV6+IV7 + PETotal, data = dat)
summary(ModelPE5) 
#n.s.

#P-E Process does not predict DV5

## DV6 Skip because already significant####
```

**What are the conditions that determine whether P vs E approaches are more or less effective?**
```{r}
#####################
#Two-Way ANOVA
#####################

#Create new categorical variables for IV1, IV3, IV4, IV5, and IV6, and IV7 to work with PE Group
#Cut at the mean

#Agent Total
summary(dat$IV1) #4.46
dat$IV1Di <- cut(dat$IV1,
                   breaks = c(-Inf, 4.46, Inf),
                   levels = c(1,2),
                   labels = c("L", "H"))

summary(dat$IV1Di) 

#IV3
summary(dat$IV3) #4.03
dat$IV3Di <- cut(dat$IV3,
                        breaks = c(-Inf, 4.03, Inf),
                        levels = c(1,2),
                        labels = c("W", "E"))

#IV4
summary(dat$IV4) #3.84
dat$IV4Di <- cut(dat$IV4,
                 breaks = c(-Inf, 3.84, Inf),
                 levels = c(1,2),
                 labels = c("W", "E"))

#IV5
summary(dat$IV5) #4.03
dat$IV5Di <- cut(dat$IV5,
                 breaks = c(-Inf, 4.03, Inf),
                 levels = c(1,2),
                 labels = c("H", "L")) #lower scores higher demands

#IV6
summary(dat$IV6) #4.37
dat$IV6Di <- cut(dat$IV6,
                 breaks = c(-Inf, 4.37, Inf),
                 levels = c(1,2),
                 labels = c("L", "T"))

#IV7
summary(dat$IV7) #4.51
dat$IV7Di <- cut(dat$IV7,
                 breaks = c(-Inf, 4.51, Inf),
                 levels = c(1,2),
                 labels = c("L", "H"))

#DV7_QualiPE
summary(dat$DV7_QualiPE) #as expected, it is pretty low
#also do not have enough people to run 2 way ANOVA 


############  DV1 #############

##### IV1xPE
lmIV11 <- lm(DV1~PEGroup*IV1Di, data = dat, weights = PEWts)
summary(lmIV11)
#n.s.
#No interaction here

##### IV3 x PE
lmIV31 <- lm(DV1~PEGroup*IV3Di, data = dat, weights = PEWts)
summary(lmIV31)
#n.s.

##### IV4 x PE
lmIV41 <- lm(DV1~PEGroup*IV4Di, data = dat, weights = PEWts)
summary(lmIV41)
#n.s.

##### IV5 x PE
lmIV51 <- lm(DV1~PEGroup*IV5Di, data = dat, weights = PEWts)
summary(lmIV51)
#significant, but seems like main effect, not interaction
Anova(lmIV51, type = 3)
#n.s. for interaction


##### IV6 x PE
lmIV61 <- lm(DV1~PEGroup*IV6Di, data = dat,weights = PEWts)
summary(lmIV61)
#n.s.

##### IV7 x PE
lmIV71 <- lm(DV1~PEGroup*IV7Di, data = dat, weights = PEWts)
summary(lmIV71)
#n.s.


############  DV2 #############

##### IV1xPE
lmIV12 <- lm(DV2~PEGroup*IV1Di, data = dat, weights = PEWts)
summary(lmIV12)
#n.s.
#No interaction here

##### IV3 x PE
lmIV32 <- lm(DV2~PEGroup*IV3Di, data = dat, weights = PEWts)
summary(lmIV32)
#Significant, main effect for IV3
Anova(lmIV32, type = 3)

##### IV4 x PE
lmIV42 <- lm(DV2~PEGroup*IV4Di, data = dat, weights = PEWts)
summary(lmIV42)
#ns

##### IV5 x PE
lmIV52 <- lm(DV2~PEGroup*IV5Di, data = dat, weights = PEWts)
summary(lmIV52)
#n.s.


##### IV6 x PE
lmIV62 <- lm(DV2~PEGroup*IV6Di, data = dat, weights = PEWts)
summary(lmIV62)
#n.s.

##### IV7 x PE
lmIV72 <- lm(DV2~PEGroup*IV7Di, data = dat, weights = PEWts)
summary(lmIV72)
#n.s.

############  DV3 #############

##### IV1 x PE
lmIV13 <- lm(DV3~PEGroup*IV1Di, data = dat,weights = PEWts)
summary(lmIV13)
#significant but main effect?
Anova(lmIV13, type = 3)
#yep, just main effect

##### IV3 x PE
lmIV33 <- lm(DV3~PEGroup*IV3Di, data = dat, weights = PEWts)
summary(lmIV33)
#n.s.

##### IV4 x PE
lmIV43 <- lm(DV3~PEGroup*IV4Di, data = dat, weights = PEWts)
summary(lmIV43)
#n.s.

##### IV5 x PE
lmIV53 <- lm(DV3~PEGroup*IV5Di, data = dat, weights = PEWts)
summary(lmIV53)
#n.s.


##### IV6 x PE
lmIV63 <- lm(DV3~PEGroup*IV6Di, data = dat, weights = PEWts)
summary(lmIV63)
#n.s.

##### IV7 x PE
lmIV73 <- lm(DV3~PEGroup*IV7Di, data = dat, weights = PEWts)
summary(lmIV73)
#n.s.


############  DV4 #############

##### IV1 x PE
lmIV14 <- lm(DV4~PEGroup*IV1Di, data = dat, weights = PEWts)
summary(lmIV14)
#n.s.

##### IV3 x PE
lmIV34 <- lm(DV4~PEGroup*IV3Di, data = dat, weights = PEWts)
summary(lmIV34)
#n.s.

##### IV4 x PE
lmIV44 <- lm(DV4~PEGroup*IV4Di, data = dat, weights = PEWts)
summary(lmIV44)
#n.s.

##### IV5 x PE
lmIV54 <- lm(DV4~PEGroup*IV5Di, data = dat, weights = PEWts)
summary(lmIV54)
#Significant, but not for interaction


##### IV6 x PE
lmIV64 <- lm(DV4~PEGroup*IV6Di, data = dat, weights = PEWts)
summary(lmIV64)
#n.s.

##### IV7 x PE
lmIV74 <- lm(DV4~PEGroup*IV7Di, data = dat, weights = PEWts)
summary(lmIV74)
Anova(lmIV74)
#n.s.

############  DV5 #############

##### IV1 x PE
lmIV15 <- lm(DV5~PEGroup*IV1Di, data = dat, weights = PEWts)
summary(lmIV15)
#n.s.

##### IV3 x PE
lmIV35 <- lm(DV5~PEGroup*IV3Di, data = dat, weights = PEWts)
summary(lmIV35)
#n.s.

##### IV4 x PE
lmIV45 <- lm(DV5~PEGroup*IV4Di, data = dat, weights = PEWts)
summary(lmIV45)
#n.s.


##### IV5 x PE
lmIV55 <- lm(DV5~PEGroup*IV5Di, data = dat, weights = PEWts)
summary(lmIV55)
#n.s.


##### IV6 x PE
lmIV65 <- lm(DV5~PEGroup*IV6Di, data = dat)
summary(lmIV65)
#n.s.

##### IV7 x PE
lmIV75 <- lm(DV5~PEGroup*IV7Di, data = dat)
summary(lmIV75)
#Interaction is significant
Anova(lmIV75, type = 3) 
#interaction no longer significant

############  DV6 #############

##### IV1 x PE
lmIV16 <- lm(DV6~PEGroup*IV1Di, data = dat)
summary(lmIV16)
#Significant but not interaction

##### IV3 x PE
lmIV36 <- lm(DV6~PEGroup*IV3Di, data = dat)
summary(lmIV36)
#Significant but not interaction
Anova(lmIV36, type = 3)

##### IV4 x PE
lmIV46 <- lm(DV6~PEGroup*IV4Di, data = dat)
summary(lmIV46)
#Significant w interaction
Anova(lmIV46, type = 3)
#not anymore

##### IV5 x PE Contextual Challenge & Demands
lmIV56 <- lm(DV6~PEGroup*IV5Di, data = dat)
summary(lmIV56)
#Significant and there might be and interaction
Anova(lmIV56)
#Yesss there is an interaction effect finally

#Create interaction plot
emm56 <- emmeans(object = lmIV56,
                 specs = ~PEGroup:IV5Di)
emmip(object = emm56,
     formula = PEGroup~IV5Di,
     CIs = TRUE)

#In low contextual challenge and demand, prescriptive is the most efficient 
#while Elicitive is the least
#In high contextual challenge and demand, the efficiency is not different among approaches

##### IV6 x PE 
lmIV66 <- lm(DV6~PEGroup*IV6Di, data = dat)
summary(lmIV66)
#Significant 
Anova(lmIV66, type = 3)
#interaction significant at the p <.01 level

#Create interaction plot
emm66 <- emmeans(object = lmIV66,
                 specs = ~PEGroup:IV6Di)
emmip(object = emm66,
      formula = PEGroup~IV6Di,
      CIs = TRUE)
#in low cultural constraints with looser norms
# prescriptive methods and hybrid are more efficient than elicitive
#in high cultural constraints with tighter norms, elicitive is the most efficient



##### IV7 x PE 
lmIV76 <- lm(DV6~PEGroup*IV7Di, data = dat)
summary(lmIV76)
#Significant 
Anova(lmIV76, type = 3)
#interaction significant at the p =.05 level

#Create interaction plot
emm76 <- emmeans(object = lmIV76,
                 specs = ~PEGroup:IV7Di)
emmip(object = emm76,
      formula = PEGroup~IV7Di,
      CIs = TRUE)
#So confused about this
#so when Agent has high tolerance for ambiguity, elicitive process would be much less efficient
#compared to hybrid and prescriptive
# Actually nvm it makes sense now; they are just too chill


############  DV8 #############

##### IV1 x PE
lmIV18 <- lm(DV8_QualiGenEff~PEGroup*IV1Di, data = dat)
summary(lmIV18)
#n.s.

##### IV3 x PE
lmIV38 <- lm(DV8_QualiGenEff~PEGroup*IV3Di, data = dat)
summary(lmIV38)
#n.s.

##### IV4 x PE
lmIV48 <- lm(DV8_QualiGenEff~PEGroup*IV4Di, data = dat)
summary(lmIV48)
#n.s.


##### IV5 x PE
lmIV58 <- lm(DV8_QualiGenEff~PEGroup*IV5Di, data = dat)
summary(lmIV58)
#n.s.


##### IV6 x PE
lmIV68 <- lm(DV8_QualiGenEff~PEGroup*IV6Di, data = dat)
summary(lmIV68)
#n.s.

##### IV7 x PE
lmIV78 <- lm(DV8_QualiGenEff~PEGroup*IV7Di, data = dat)
summary(lmIV78)
#Interaction might be significant
Anova(lmIV78, type = 3) 
#interaction is significant at p = .05

#Create interaction plot
emm78 <- emmeans(object = lmIV78,
                 specs = ~PEGroup:IV7Di)
emmip(object = emm78,
      formula = ~PEGroup:IV7Di,
      CIs = TRUE)
#When agent has low tolerance for ambiguity
#hybrid is significantly less effective than prescriptive or elicitive (coded)
#when agent has high tolerance for ambiguity
#hybrid or elicitive is coded to be much more effective


############  DV9 #############

##### IV1 x PE
lmIV19 <- lm(DV9_QualiSustain~PEGroup*IV1Di, data = dat)
summary(lmIV19)
#n.s.

##### IV3 x PE
lmIV39 <- lm(DV9_QualiSustain~PEGroup*IV3Di, data = dat)
summary(lmIV39)
#n.s.

##### IV4 x PE
lmIV49 <- lm(DV9_QualiSustain~PEGroup*IV4Di, data = dat)
summary(lmIV49)
#n.s.


##### IV5 x PE
lmIV59 <- lm(DV9_QualiSustain~PEGroup*IV5Di, data = dat)
summary(lmIV59)
#n.s.


##### IV6 x PE
lmIV69 <- lm(DV9_QualiSustain~PEGroup*IV6Di, data = dat)
summary(lmIV69)
#n.s.

##### IV7 x PE
lmIV79 <- lm(DV9_QualiSustain~PEGroup*IV7Di, data = dat)
summary(lmIV79)
#n.s.
```

**Cont What are the conditions that determine whether P vs E approaches are more or less effective?**
```{r}
#########################
#Moderation Analysis
##########################

#Running PE as a continuous variable 

####IV1
ModelPE11 <- lm(DV1~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE11) #Interaction not significant, not a moderator for DV1

ModelPE21 <- lm(DV2~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE21) #N.S

ModelPE31 <- lm(DV3~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE31) #Interaction not significant, not a moderator for DV3

ModelPE41 <- lm(DV4~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE41) #Interaction not significant, not a moderator for DV4

ModelPE51 <- lm(DV5~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE51) #Interaction not significant, not a moderator for DV5

ModelPE61 <- lm(DV6~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE61) #Interaction not significant, not a moderator for DV6

ModelPE81 <- lm(DV8_QualiGenEff~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE81)

ModelPE91 <- lm(DV9_QualiSustain~IV1Di + PETotal + IV1Di:PETotal, data = dat)
summary(ModelPE91)

#IV1 does not have an effect on P-E Approach to effectiveness

####IV3
ModelPE13 <- lm(DV1~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE13) #Interaction not significant, not a moderator for DV1

ModelPE23 <- lm(DV2~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE23) #N.S

ModelPE33 <- lm(DV3~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE33) #Interaction not significant, not a moderator for DV3

ModelPE43 <- lm(DV4~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE43) #Interaction not significant, not a moderator for DV4

ModelPE53 <- lm(DV5~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE53) #Interaction not significant, not a moderator for DV5

ModelPE63 <- lm(DV6~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE63) #Interaction  significant finally at the p <.01 lvl

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV6,
                color = IV3Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Efficiency",
       color = "Stakeholder Value Orientation") +
  geom_smooth(method = "lm") #turn it into lines
#if want to remove the SE shadows, add se = F after method = "lm"
#If stakeholder have more western values, prescriptive methods are more efficient
#if stakeholder have more eastern values, elicitive are more efficient


ModelPE83 <- lm(DV8_QualiGenEff~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE83) #ns

ModelPE93 <- lm(DV9_QualiSustain~IV3Di + PETotal + IV3Di:PETotal, data = dat)
summary(ModelPE91) #ns

####IV4
ModelPE14 <- lm(DV1~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE14) #Interaction not significant, not a moderator for DV1

ModelPE24 <- lm(DV2~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE24) #N.S

ModelPE34 <- lm(DV3~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE34) #Interaction not significant, not a moderator for DV3

ModelPE44 <- lm(DV4~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE44) #Interaction not significant, not a moderator for DV4

ModelPE54 <- lm(DV5~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE54) #Interaction not significant, not a moderator for DV5

ModelPE64 <- lm(DV6~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE64) #Interaction is significant at p<.01 level

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV6,
                color = IV4Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Efficiency",
       color = "Agent Value Orientation") +
  geom_smooth(method = "lm") #turn it into lines
#If agent have more western values, prescriptive methods are more efficient
#if agent have more eastern values,there is no significant difference in approach and outcomes
#although elicitive is slightly better

ModelPE84 <- lm(DV8_QualiGenEff~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE84) #ns

ModelPE94 <- lm(DV9_QualiSustain~IV4Di + PETotal + IV4Di:PETotal, data = dat)
summary(ModelPE94) #ns

####IV5
ModelPE15 <- lm(DV1~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE15) #Interaction is significant at p =.04

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV1,
                color = IV5Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Self-Rated Effectiveness",
       color = "Contextual Challenges & Demands") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#In context with low demand and challenges, prescriptive methods are more effective
#in context with high demand and challenges, elicitive methods are more effective

ModelPE25 <- lm(DV2~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE25) #N.S

ModelPE35 <- lm(DV3~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE35) #Interaction not significant, not a moderator for DV3

ModelPE45 <- lm(DV4~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE45) #Interaction not significant, not a moderator for DV4

ModelPE55 <- lm(DV5~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE55) #Interaction not significant, not a moderator for DV5

ModelPE65 <- lm(DV6~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE65) 
#Interaction significant at p <.01, but already got from 2 way anova

ModelPE85 <- lm(DV8_QualiGenEff~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE85) #ns

ModelPE95 <- lm(DV9_QualiSustain~IV5Di + PETotal + IV5Di:PETotal, data = dat)
summary(ModelPE95) #ns


####IV6
ModelPE16 <- lm(DV1~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE16) #Interaction not significant, not a moderator for DV1

ModelPE26 <- lm(DV2~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE26) #N.S

ModelPE36 <- lm(DV3~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE36) #Interaction not significant, not a moderator for DV3

ModelPE46 <- lm(DV4~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE46) #Interaction not significant, not a moderator for DV4

ModelPE56 <- lm(DV5~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE56) #Interaction not significant, not a moderator for DV5

ModelPE66 <- lm(DV6~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE66) #Interaction significant, already knew from 2 way anova

ModelPE86 <- lm(DV8_QualiGenEff~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE86) #ns

ModelPE96 <- lm(DV9_QualiSustain~IV6Di + PETotal + IV6Di:PETotal, data = dat)
summary(ModelPE96) #ns

####IV7
ModelPE17 <- lm(DV1~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE17) #Interaction significant at the p <.001 lvl

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV1,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Self-Rated Effectiveness",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is the most effective
#when agent has high TA, elicitive is the most effective

ModelPE27 <- lm(DV2~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE27) #Significant at the p <.001 level

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV2,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Self-Rated Cultural Appropriateness",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is the most culturally appropriate
#when agent has high TA, elicitive is the most culturally appropriate

ModelPE37 <- lm(DV3~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE37) #Interaction is significant at p <.01 level

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV3,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Sustainability",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is more sustainable
#when agent has high TA, elicitive is more sustainable

ModelPE47 <- lm(DV4~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE47) #Significant at the p <.01 level

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV4,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Cultural Sensitivity",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is more culturally sensitive
#when agent has high TA, elicitive is more culturally sensitive

ModelPE57 <- lm(DV5~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE57) #Significant, not a moderator for DV5

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV5,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Cost Effectiveness",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is more cost effective
#when agent has high TA, elicitive is more cost effective, but not that much of difference

ModelPE67 <- lm(DV6~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE67) #Significant, already with 2 way ANOVA

ModelPE87 <- lm(DV8_QualiGenEff~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE87) #significant at the p <.001 level

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV8_QualiGenEff,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Coded Effectiveness",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is coded to be slightly more effective
#when agent has high TA, elicitive is coded to be much more effective

ModelPE97 <- lm(DV9_QualiSustain~IV7Di + PETotal + IV7Di:PETotal, data = dat)
summary(ModelPE97) #significant at the p = .03 lvl

#Create interaction plot
ggplot(dat, aes(x = PETotal,
                y = DV9_QualiSustain,
                color = IV7Di)) +
  theme_bw() +
  labs(x = "P to E",
       y = "Coded Sustainability",
       color = "Agent Tolerance for Ambiguity") +
  geom_smooth(method = "lm",
              se = F) #turn it into lines
#When agent has low TA, prescriptive is coded to be more sustainable
#when agent has high TA, elicitive is coded to be more sustainable
```